Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
editing previous lemma

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps in the proof of the main theorem: Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
}{\beta}P}$ from those of $R_{\halfcan'}$, where
%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$\halfcan \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. \todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.  There are too many clauses...}
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors, although even Lemma
%~\ref{lem:raise-stacky-order} has certain generalizations, as noted
%in Remark ~\ref{rem:raise-fractional-order}

@@

\iffalse{
Lemma \ref{lem:sat-1} leads to the the following corollaries.
\todo{do we want this here?}
\begin{cor}\label{cor-gen-0-with-log}
If $(\sx, \halfcan, \Delta)$ is a stacky curve with signature $(g; e_1, \ldots, e_n; \delta)$ with $g=0$ and $\delta>0$, then $R_\halfcan$ is generated in degree at most $e=\max(e_i)$ with relations generated in degree at most $2e$.
\end{cor}
\begin{proof}
By remark \ref{rem:delta-not-1}, $\delta\ge 2$ so $\halfcan$ is linearly equivalent to an effective divisor.  Thus, we can recursively apply Lemma \ref{lem:sat-1} to prove the corollary.
\end{proof}
}\fi

>>>>

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps in the proof of the main theorem: Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
}{\beta}P}$ from those of $R_{\halfcan'}$, where
%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$\halfcan \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. \todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.  There are too many clauses...}
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors.

@@
